Hypoglycemia Analysis - CFRD REMOVED

### 2023-04-04 Christine Chan/Hypoglycemia/tim_analysis_no_CFRD.Rmd
rename tim analysis

table_dat$CF_hypo_60[table_dat$CF == "Yes" & table_dat$hypo_60 == "Yes"] <- "CF/Hypo"
table_dat$CF_hypo_60[table_dat$CF == "Yes" & table_dat$hypo_60 == "No"] <- "CF/No-Hypo"
table_dat$CF_hypo_60[table_dat$CF == "No" & table_dat$hypo_60 == "Yes"] <- "No-CF/Hypo"
table_dat$CF_hypo_60[table_dat$CF == "No" & table_dat$hypo_60 == "No"] <- "No-CF/No-Hypo"

table_dat$CF_hypo_70[table_dat$CF == "Yes" & table_dat$hypo_70 == "Yes"] <- "CF/Hypo"
table_dat$CF_hypo_70[table_dat$CF == "Yes" & table_dat$hypo_70 == "No"] <- "CF/No-Hypo"
table_dat$CF_hypo_70[table_dat$CF == "No" & table_dat$hypo_70 == "Yes"] <- "No-CF/Hypo"
table_dat$CF_hypo_70[table_dat$CF == "No" & table_dat$hypo_70 == "No"] <- "No-CF/No-Hypo"

@@

- matsuda now significant on ANOVA with Hypo < 60
- OGTT Category pairwise comparison CF/Hypo60 vs CF/No-Hypo60 now significant
- HOMA-IR pairwise comparison CF/Hypo60 vs No-CF/No-Hypo60 now significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo60 vs No-CF/Hypo60 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo60 vs No-CF/No-Hypo60 no longer significant
- CGM MAG CF/No-Hypo60 vs No-CF/Hypo60 now significant
- Matsuda and Homa-IR pairwise comparisons CF/Hypo70 vs No-CF/No-Hypo70 now significant
- Delta Glucagon pairwise comparison CF/No-Hypo70 vs No-CF/Hypo70 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo70 vs No-CF/Hypo70 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo70 vs No-CF/No-Hypo70 no longer significant
- %time over 140 pairwise comparison CF/Hypo70 vs CF/No-Hypo no longer significant

@@

kbl(ptab, caption = "Pairwise p-values") %>%
  column_spec(2, background = 
                ifelse(ptab$`CF/Hypo vs CF/No-Hypo` < 0.05, "red", "white")) %>%
  column_spec(3, background = 
                na.fill(ifelse(ptab$`CF/Hypo vs No-CF/Hypo` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(4, background = 
                na.fill(ifelse(ptab$`CF/Hypo vs No-CF/No-Hypo` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(5, background = 
                na.fill(ifelse(ptab$`CF/No-Hypo vs No-CF/Hypo` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(6, background = 
                na.fill(ifelse(ptab$`CF/No-Hypo vs No-CF/No-Hypo` < 0.05, 
                               "red", "white"), "white)"))
```

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "No-CF/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "No-CF/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "No-CF/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "No-CF/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "No-CF/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "No-CF/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "No-CF/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "No-CF/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "No-CF/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "No-CF/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

@@

@@

>>>>

table_dat$CF_hypo_60[table_dat$CF == "Yes" & table_dat$hypo_60 == "Yes"] <- "CF/Hypo"
table_dat$CF_hypo_60[table_dat$CF == "Yes" & table_dat$hypo_60 == "No"] <- "CF/No-Hypo"
table_dat$CF_hypo_60[table_dat$CF == "No" & table_dat$hypo_60 == "Yes"] <- "HC/Hypo"
table_dat$CF_hypo_60[table_dat$CF == "No" & table_dat$hypo_60 == "No"] <- "HC/No-Hypo"

table_dat$CF_hypo_70[table_dat$CF == "Yes" & table_dat$hypo_70 == "Yes"] <- "CF/Hypo"
table_dat$CF_hypo_70[table_dat$CF == "Yes" & table_dat$hypo_70 == "No"] <- "CF/No-Hypo"
table_dat$CF_hypo_70[table_dat$CF == "No" & table_dat$hypo_70 == "Yes"] <- "HC/Hypo"
table_dat$CF_hypo_70[table_dat$CF == "No" & table_dat$hypo_70 == "No"] <- "HC/No-Hypo"

@@

- matsuda now significant on ANOVA with Hypo < 60
- OGTT Category pairwise comparison CF/Hypo60 vs CF/No-Hypo60 now significant
- HOMA-IR pairwise comparison CF/Hypo60 vs HC/No-Hypo60 now significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo60 vs HC/Hypo60 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo60 vs HC/No-Hypo60 no longer significant
- CGM MAG CF/No-Hypo60 vs HC/Hypo60 now significant
- Matsuda and Homa-IR pairwise comparisons CF/Hypo70 vs HC/No-Hypo70 now significant
- Delta Glucagon pairwise comparison CF/No-Hypo70 vs HC/Hypo70 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo70 vs HC/Hypo70 no longer significant
- CGM Avg Glucose pairwise comparison CF/No-Hypo70 vs HC/No-Hypo70 no longer significant
- %time over 140 pairwise comparison CF/Hypo70 vs CF/No-Hypo no longer significant

@@

kbl(ptab, caption = "Pairwise p-values") %>%
  column_spec(2, background = 
                ifelse(ptab$`CF/Hypo vs CF/No-Hypo` < 0.05, "red", "white")) %>%
  column_spec(3, background = 
                na.fill(ifelse(ptab$`CF/Hypo vs HC/Hypo` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(4, background = 
                na.fill(ifelse(ptab$`CF/Hypo vs HC/No-Hypo` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(5, background = 
                na.fill(ifelse(ptab$`CF/No-Hypo vs HC/Hypo` < 0.05, 
                               "red", "white"), "white)")) %>%
  column_spec(6, background = 
                na.fill(ifelse(ptab$`CF/No-Hypo vs HC/No-Hypo` < 0.05, 
                               "red", "white"), "white)"))
```

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60, color = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_60)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70, color = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r, warning = F, message = F}
p1 <- ggplot(data = table_dat, aes(y = matsuda_ins, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "Matsuda Index", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(45, 50),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(data = table_dat, aes(y = homa_ir, x = CF_hypo_70)) +
  geom_boxplot() +
  labs(y = "HOMA IR", x = "", color = "") +
  geom_signif(
    comparisons = list(c("CF/Hypo", "CF/No-Hypo"), c("CF/Hypo", "HC/No-Hypo")),
    color = "black",
    y_position = c(4.5, 5),
    test = "wilcox.test",
    map_signif_level = function(p) sprintf("p = %.2g", p)
  ) +
  theme_light() +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r fig.height=5, results="asis"}
outcomes <- c(
  "daytime_avg_sensor_glucose",
  "percent_time_under_60",
  "percent_time_under_70",
  "percent_time_over_140",
  "percent_time_over_180",
  "daytime_sd",
  "cov",
  "mag"
)
outcomes_labs <- c(
  "Avg Glucose (Daytime) [mg/dL]",
  "% Time Under 60 (mg/dL)",
  "% Time Under 70 (mg/dL)",
  "% Time Over 140 (mg/dL)",
  "% Time Over 180 (mg/dL)",
  "SD",
  "COV",
  "MAG"
)

@@

  cat("\n")
  cat(paste("###", outcomes_labs[i]))
  cat("\n")
  print(p70 + p60)
  cat("\n")
}
```

@@

# Tim's additional changes for reviewer 1

```{r}
# Plot
ggplot(data = cgm_table_dat, aes_string(y = "percent_time_under_70", x = "CF_hypo_70")) +
  labs(y = "% Time Under 70 (mg/dL)", x = "") +
  geom_jitter(alpha = 0.5, width = 0.1) +
  geom_boxplot(alpha = 0.5, outlier.alpha = 0) +
  geom_hline(yintercept=4.1, linetype="dashed")+
  annotate("text",x=4.4, y=4.5, label="4.1 %") +
  theme_light() +
  ggtitle("Hypoglycemia by OGTT (< 70)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r results='asis'}
# Comparisons
cgm_table_dat$perc_time_70_thresh = cut(cgm_table_dat$percent_time_under_70,
                                        breaks = c(-Inf,4.1,Inf),
                                        labels = c("No","Yes"))
t = tableby(CF_hypo_70~fe(perc_time_70_thresh),data = cgm_table_dat)
summary(t,pfootnote = T,
        labelTranslations = 
          list(perc_time_70_thresh="Percent time under 70 mg/dL > 4.1%"))
```

```{r results='asis'}
cgm_table_dat$CF = factor(cgm_table_dat$CF,levels = c("Yes","No"),labels = c("CF","HC"))
t = tableby(CF~fe(perc_time_70_thresh),data = cgm_table_dat)
summary(t,pfootnote = T,
        labelTranslations = 
          list(perc_time_70_thresh="Percent time under 70 mg/dL > 4.1%"))
```
